Performance of two different ontological and data access methods

### 2015-03-05 cold2014/magnus.tex
Rewrite the text around figures in experiment setup
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1043 43ef1190-90fd-4dd7-a769-d0121f02b80e

After each request we saved the run plus
the response time and wrote it to file on CSV format. To evaluate the
result we used the programming language R with the packages
\textsf{DoE.base}~\cite{DoEBase}, \textsf{FrF2}~\cite{FrF2} and
\textsf{BsMD}~\cite{BsMD}. R allowed us to parse the CSV files created
from the experiments and output them in two types of graphs.

To evaluate the graphs we have used a method in the \textsf{FrF2} R
package called \textsf{DanielPlot} to create half-normal plots. The
intuition behind this is simple: If errors are normally distributed,
which is a conservative assumption, and there are no significant
effects they will also be normally distributed, and so the estimated
effects would end up on a straight line. Any significant deviations
from a straight line indicates a significant factor.  That we use a
half-normal plot (rather than a normal plot) means that
the most significant effects will end up in the top right
corner. 
%
\begin{wraptable}{r}{0.35\textwidth}
\vspace{-35pt}
    \begin{tabular}{ | l | l |}
    \hline
    {\bf Factor} & {\bf Abbrev} \\ \hline
   Ontology & \textsf{O} \\
   Fuel Type & \textsf{FT} \\
   Transmission & \textsf{T} \\
   Weight & \textsf{W} \\
   Total Weight & \textsf{WT} \\
   Emission & \textsf{E} \\
   \# of Gears & \textsf{G} \\
   Seating Capacity & \textsf{SC} \\
   Fuel Consumption & \textsf{FC} \\
   Doors & \textsf{D} \\
\hline
    \end{tabular}
\caption{Factors and their abbreviation}\label{facandabbrev}
\vspace{-45pt}
\end{wraptable}
%
The axes themselves are not important to understand the plot
nor the results, refer to \cite{PlanExp} for details.  We have also
set the significance level at $\alpha = 0.05$, where
\textsf{DanielPlot} is using Lenth's method for the analysis of
unreplicated factorials.

For brevity, we will use abbreviations given in Table~\ref{facandabbrev}.

@@

Figure~\ref{3factorGraph} shows only one significant factor, namely
the \textsf{O} factor in the upper right corner. In
Table~\ref{3factorEffect} we can see the time effects from largest to
smallest.  We see that the ontology factor has the largest effect on
approximately 2.2 seconds which means that one of the ontologies
overall is 2.2 seconds faster. By reading the results from the linear
model it is the factor level \textsf{-vso} which has an overall faster
response time.

@@

In Figure~\ref{10factorGraph} we can see the results from running
all the 1024 runs.  We can see that there are a lot of significant
effects present here. 
Unfortunately there are so many significant factors that there are
some of them that are illegible, but most of them have a low impact on
the significance graph.  In Table~\ref{10factorEffect} we can see the top
fifteen absolute effects. We can see that emission and fuel consumption are 
the most significant factors besides the ontology factor.
The linear model again tells us that the option
\textsf{-vso} has a significantly lower response time than
\textsf{-co}.

>>>>

After each request we saved the run plus
the response time and wrote it to file on CSV format. To evaluate the
result we used the programming language R with the packages
\textsf{DoE.base}~\cite{DoEBase}, \textsf{FrF2}~\cite{FrF2} and
\textsf{BsMD}~\cite{BsMD}. R allowed us to parse the CSV files created
from the experiments for further study.

The \textsf{FrF2} R package implements a criterion of significance
known as Lenth's method, which we have used with a significance level at $\alpha =
0.05$. % TODO: Kan slenge med referanse
%
\begin{wraptable}{r}{0.35\textwidth}
\vspace{-35pt}
    \begin{tabular}{ | l | l |}
    \hline
    {\bf Factor} & {\bf Abbrev} \\ \hline
   Ontology & \textsf{O} \\
   Fuel Type & \textsf{FT} \\
   Transmission & \textsf{T} \\
   Weight & \textsf{W} \\
   Total Weight & \textsf{WT} \\
   Emission & \textsf{E} \\
   \# of Gears & \textsf{G} \\
   Seating Capacity & \textsf{SC} \\
   Fuel Consumption & \textsf{FC} \\
   Doors & \textsf{D} \\
\hline
    \end{tabular}
\caption{Factors and their abbreviation}\label{facandabbrev}
\vspace{-45pt}
\end{wraptable}
%
For brevity, we will use abbreviations given in Table~\ref{facandabbrev}.

@@

Using the Lenth criterion, we find only one significant factor, namely
the \textsf{O} factor. In Table~\ref{3factorEffect} we can see the
time effects from largest to smallest.  We see that the ontology
factor has the largest effect on approximately 2.2 seconds which means
that one of the ontologies overall is 2.2 seconds faster. By reading
the results from the linear model it is the factor level \textsf{-vso}
which has an overall faster response time.

@@

There is a large number of significant effects when we employ Lenth's
method on this large experiment. In Table~\ref{10factorEffect} we have
included the top fifteen absolute effects. We can see that emission
and fuel consumption are the most significant factors besides the
ontology factor.  The linear model again tells us that the option
\textsf{-vso} has a significantly lower response time than
\textsf{-co}.
